\vfill A Testing Framework for Web Applications

### 2014-02-07 Paper/paper.tex
More done.... More to do.

\subsubsection{\cite{TestingWebServicesSurvey}}

@@

\subsubsection{``Going Faster: Testing The Web Application'' \cite{GoingFaster}}
Two employees of Evant Software wrote an article for IEEE Software regarding the testing of web applications. Mostly this paper was an overview and implementation of Test Driven Development (TDD) and eXtreme Programming, but in the middle of the article was a good section about the difficulties of testing the web and how to deal them. Some of the most useful advice was: ``First, test those parts of the server-side code that are not directly concerned with being part of the Web application, without involving Web peculiarities. ... Second, test those parts of the client-side code that have no server interaction. This is typically code that contains little or no business logic. ... Third, write functional tests of a low grain in the server-side language (for example, Java or C++) that simulate the request/response Web environment. ... Using this framework you can write walk-through tests that simulate the user moving through the UI''.

TALK ABOUT WHAT MAKES THIS NICE

>>>>

\subsubsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications.

@@

MORE MORE MORE MORE

\subsubsection{``Going Faster: Testing The Web Application'' \cite{GoingFaster}}
Two employees of Evant Software wrote an article for IEEE Software regarding the testing of web applications. Mostly this paper was an overview and implementation of Test Driven Development (TDD) and eXtreme Programming, but in the middle of the article was a good section about the difficulties of testing the web and how to deal them. A few of the remarks regarding the difficulty of web testing is that often the client-side and server-side portions of web applications are written in different languages. This wasn't an issue for our application, but is still an issue for many applications. Some of the most useful advice was: ``First, test those parts of the server-side code that are not directly concerned with being part of the Web application, without involving Web peculiarities. ... Second, test those parts of the client-side code that have no server interaction. This is typically code that contains little or no business logic. ... Third, write functional tests of a low grain in the server-side language (for example, Java or C++) that simulate the request/response Web environment. ... Using this framework you can write walk-through tests that simulate the user moving through the UI''.

This step-by-step walkthrough of how to test was an excellent starting point to look at different tools and how they handled this issue.
